A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Save a line
Space freeup in section 3

The parser uses two auxiliary data structures: a stack $S$ of partially completed subtrees and a buffer $B$ of tokens yet to be parsed. The parser is initialized with the stack empty and with the buffer containing the tokens $\mathbf x$ of the sentence in order. Let $\langle S, B \rangle = \langle \emptyset, \mathbf x \rangle$ denote this starting state. We next proceed through the transition sequence, where each transition $t_t$ selects one of the two following operations. Below the $\mid$ symbol denotes the \textit{cons} (concatenation) operator. We arbitrarily choose to always \textit{cons} on the left in the notation below.
\begin{description}
  \item[\shift:] $\langle S, x \mid B \rangle \to \langle x \mid S, B \rangle$. This operation pops an element from the buffer and pushes it onto the top of the stack.
  \item[\reduce:] $\langle x \mid y \mid S, B \rangle \to \langle (x, y) \mid S, B \rangle$. This operation pops the top two elements from the stack, merges them into a binary tree with children $(x, y)$, and pushes the result back onto the stack.
\end{description}

@@

\paragraph{The composition function}
When a \reduce~operation is performed, the vector representations of two tree nodes are popped off of the head of the stack and fed into a {\it composition function}, which is a neural network function that produces a representation for a new tree node that is the parent of the two popped nodes. This new node is then pushed on to the stack.

The TreeLSTM composition function \citep{tai2015improved} generalizes the LSTM neural network layer to tree- rather than sequence-based inputs, and it shares with the LSTM the idea of representing intermediate states as a pair of a fast-changing state representation $\vec{h}$ and a slower-changing memory representation $\vec{c}$. Our version is formulated as:
\begin{gather}
\colvec{5}
    {\vec{i}}
    {\vec{f}_l}
    {\vec{f}_r}
    {\vec{o}}
    {\vec{g}}
= \colvec{5}
    {\sigma}
    {\sigma}
    {\sigma}
    {\sigma}
    {\text{tanh}}
\left(
W_{\text{comp}}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
+ \vec{b}_{\text{comp}}
\right) \label{eqn:lstm1}
\\
\vec{c} = \vec{f}_l \odot \vec{c}_s^{\,2} + \vec{f}_r \odot \vec{c}_s^{\,1} + \vec{i} \odot \vec{g}  
\\
\vec{h} = \vec{o} \odot \vec{c}
\end{gather}
where $\sigma$ is the sigmoid activation function and $\odot$ is the elementwise product. The two input tree nodes popped off the stack are represented as the pairs $\langle\vec{h}^1_s, \vec{c}^{\,1}_s\rangle$ and $\langle\vec{h}^2_s, \vec{c}^{\,2}_s\rangle$. In addition, $\vec{e}$ is an optional input argument which is either the empty vector or a vector from an external source like the tracking LSTM (see Section~\ref{sec:tracking}). The result of this function is the pair $\langle\vec{h}, \vec{c}\rangle$, which is placed back on the stack. Each vector-valued variable listed here is of the same dimension $D$ except $\vec{e}$, which is of the independent dimension $D_{\text{tracking}}$.

>>>>

The parser uses two auxiliary data structures: a stack $S$ of partially completed subtrees and a buffer $B$ of tokens yet to be parsed. The parser is initialized with the stack empty and the buffer containing the tokens $\mathbf x$ of the sentence in order. Let $\langle S, B \rangle = \langle \emptyset, \mathbf x \rangle$ denote this starting state. We next proceed through the transition sequence, where each transition $t_t$ selects one of the two following operations. Below the $\mid$ symbol denotes the \textit{cons} (concatenation) operator. We arbitrarily choose to always \textit{cons} on the left in the notation below.
\begin{description}
  \item[\shift:] $\langle S, x \mid B \rangle \to \langle x \mid S, B \rangle$. This operation pops an element from the buffer and pushes it onto the top of the stack.
  \item[\reduce:] $\langle x \mid y \mid S, B \rangle \to \langle (x, y) \mid S, B \rangle$. This operation pops the top two elements from the stack, merges them into a binary tree with children $(x, y)$, and pushes the result back onto the stack.
\end{description}

@@

\paragraph{The composition function}
When a \reduce~operation is performed, the vector representations of two tree nodes are popped off of the stack and fed into a {\it composition function}, which is a neural network function that produces a representation for a new tree node that is the parent of the two popped nodes. This new node is pushed on to the stack.

The TreeLSTM composition function \citep{tai2015improved} generalizes the LSTM neural network layer to tree- rather than sequence-based inputs, and it shares with the LSTM the idea of representing intermediate states as a pair of a fast-changing state representation $\vec{h}$ and a slower-changing memory representation $\vec{c}$. Our version is formulated as:
\begin{gather}
\colvec{5}
    {\vec{i}}
    {\vec{f}_l}
    {\vec{f}_r}
    {\vec{o}}
    {\vec{g}}
= \colvec{5}
    {\sigma}
    {\sigma}
    {\sigma}
    {\sigma}
    {\text{tanh}}
\left(
W_{\text{comp}}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
+ \vec{b}_{\text{comp}}
\right) \label{eqn:lstm1}
\\
\vec{c} = \vec{f}_l \odot \vec{c}_s^{\,2} + \vec{f}_r \odot \vec{c}_s^{\,1} + \vec{i} \odot \vec{g}  
\\
\vec{h} = \vec{o} \odot \vec{c}
\end{gather}
where $\sigma$ is the sigmoid activation function and $\odot$ is the elementwise product. The pairs $\langle\vec{h}^1_s, \vec{c}^{\,1}_s\rangle$ and $\langle\vec{h}^2_s, \vec{c}^{\,2}_s\rangle$ are the two input tree nodes popped off the stack. In addition, $\vec{e}$ is an optional vector valued input argument which is either empty or from an external source like the tracking LSTM (see Section~\ref{sec:tracking}). The result of this function, the pair $\langle\vec{h}, \vec{c}\rangle$, is placed back on the stack. Each vector-valued variable listed is of the same dimension $D$ except $\vec{e}$, of the independent dimension $D_{\text{tracking}}$.
